Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-03-28 src/docs_paper/paper.Rmd
Add IS-INLA citation

Other work aiming to extend the scope of the INLA method includes the `inlabru` \textsc{R} package of @bachl2019inlabru, and the INLA within MCMC approach of @gomez2018markov, both of which leverage the `R-INLA` \textsc{R} package [@martins2013bayesian].
`inlabru` approximates non-linear predictors using linearisation, which involves making iterative calls to `R-INLA`.
<!-- See https://inlabru-org.github.io/inlabru/articles/method.html -->
<!-- Want to say in particular what the class of models that `inlabru` allows you to fit are -->
<!-- Don't know the answer to this yet, but asking Janine Illian I'm told you don't have to call R-INLA that many times -->
<!-- I think it'd obviously depend on the exact details of the problem at hand -->
INLA within MCMC is suitable for models which are LGMs conditional on some subset of the parameters being fixed.
For such models, Metropolis-Hastings style algorithms can be defined to update the fixed parameters, with acceptance probabilities calculated using by repeat calls to `R-INLA`.
<!-- It would or would not be possible to fit the Naomi model in these frameworks. -->

>>>>

Other work aiming to extend the scope of the INLA method includes the `inlabru` \textsc{R} package [@bachl2019inlabru], INLA within MCMC [@gomez2018markov], and importance sampling with INLA [@berild2022importance], all of which leverage the `R-INLA` \textsc{R} package [@martins2013bayesian].
`inlabru` approximates non-linear predictors using linearisation, which involves making iterative calls to `R-INLA`.
<!-- See https://inlabru-org.github.io/inlabru/articles/method.html -->
<!-- Want to say in particular what the class of models that `inlabru` allows you to fit are -->
<!-- Don't know the answer to this yet, but asking Janine Illian I'm told you don't have to call R-INLA that many times -->
<!-- I think it'd obviously depend on the exact details of the problem at hand -->
INLA within MCMC and importance sampling with INLA are suitable for models which are LGMs conditional on some subset of the parameters being fixed.
<!-- It would or would not be possible to fit the Naomi model in these frameworks. -->
